Using reference models in variable selection \vspace{.1in}

### 2022-01-05 reviews/rebuttal.tex

		\vspace{0.5cm}

		\fede{Moreover, the projective prediction approach for complete variable selection is not the aim of this work. The method has been included for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection. Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it not trivial to extend for the complete selection. We do not exclude that better projective prediction method for complete selection can be designed in the future.}
\end{reply}

% Point one description 
\begin{point}
My main concern with respect to the projective predictive approach is the robustness of the results to the reference model. Apparently, you can build very different references models to the same data set: have you study the sensitivity of the results with different reference models?. You use Bayesian models as reference models and, in these cases, the determination of prior distribution is not very clear. You can build hundreds and hundreds of prior distribution: for instance in (7) you can have use standard inverted gamma priors on $\tau^2$ and $\sigma^2$ by determining the parameters of the prior in order to the prior mixture gives reasonable results about the data using the prior mixture. How can you study the robustness of your results to this important aspect?
\end{point}

\begin{reply}
Thank you for your comments. We have added clarification at the end of Section 2.2 regarding the reference model, in particular we write that

\vspace{0.5cm}
\textit{
``Clearly, the reference model approach requires a sensible model. The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods. [...] In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.''
}
\vspace{0.5cm}

@@

The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues. As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
\end{reply}

%\todo
%\begin{description}
%    \item[Mans] Clarified that we present first time how this problem should be approached in the Bayesian context.
%\end{description}

\begin{point}
Perhaps a solution to the previous problem would be to determine the reference model using frequentist MLE procedures that avoid the construction of prior distributions and use a single point prediction or, alternatively, to use the sampling distribution of MLE as a posterior distribution and take this “Bayesian” model as reference model. Do you have any experience in this line?
\end{point}

\begin{reply}
Thank you for the interesting question. It is known that MLE is more unstable than Bayesian approach. The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors. We have added references that discuss merits of Bayesian approach compared to MLE. Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model.

Inspired by your question, we added a discussion of this in the new version of the paper. In Section 2.2 we write

\textit{``In general, there is not restriction on the type of model the reference models 
	should be and a sensible reference model does not need to be Bayesian.
	However, Bayesian methods can help in some of those situations
	where MLE procedures struggle. 
	It is known that as the number of parameters in the model increases, the MLE
	estimator is dominated by shrunk estimators 
	\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
	The use of a prior in Bayesian inference automatically incorporates 
	some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
	For the sake of our study, we rely on simple data structure which can be well described 
	by linear regression models. However, more complex data can arise from applications, for example including hierarchical structures. In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the posterior distribution.''}

@@

\begin{reply}
\fede{We touch the computational aspects in Section 2.2. The reference model approach has in general the additional cost of fitting a reference model. However, this is usually available when building up a model via robust workflows \citep{gelman2020bayesian}. Therefore, in these cases there is not additional cost. In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.}
\end{reply}

\begin{point}
Please add a brief summary of the results you obtained in Section 3 and the main message you infer from these results before moving onto Section 4.
\end{point}

\begin{reply}
\fede{We added a new Section 3.3 which summarises and elaborate the results of Section 3. In particular, we write:
}

\vspace{0.5cm}
\textit{
``The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case.
The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the method applied. These results are confirmed also in the real word data example with the body fat dataset. The stepwise selection achieves far better selection with the reference model approach (see Figure 5 and Table 3). However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured. Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection. Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.''
}
\vspace{0.5cm}
\end{reply}

### 2022-01-05 paper/ref_approach.tex
extended answers to reviewers

A properly designed reference model is able to filter parts of the
noise present in the data, and hence to provide an improved and more
stable selection process. This holds even if the reference model does
not perfectly resemble the true data generating process. Moreover, our
analyses indicate that the substantial reduction of variance
attributable to noise is usually more important than small potential
bias due to model misspecification.  We argue that, regardless of how
the reference model is set up and used in the inference procedure, it
can be always seen as acting as a filter on the observed
data. Furthermore, regardless of what specific model selection method
is used, a reference model can be used instead of raw data during the
selection process to improve the stability and selection
performance. Our results indicate that the core reason why the
reference model based methods perform well is the reference model
itself, rather than the specific way of using it.  In general, the
less data we have and the more complex the estimated models are, the
higher is the benefit of using a reference models as the basis for
variable selection.

@@

\fede{Clearly, the reference model approach requires a sensible model. The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods. In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.}

>>>>

A properly designed reference model is able to filter parts of the
noise present in the data, and hence to provide an improved and more
stable selection process. This holds even if the reference model does
not perfectly resemble the true data generating process. 
\fede{Clearly, the reference model approach requires a sensible model. 
The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. 
The goodness of a reference model comes from its predictive ability which should be 
assessed via proper validation methods.} Our analyses indicate that the substantial 
reduction of variance attributable to noise is usually more important than small potential
bias due to model misspecification.
\fede{When the goal is ranking the variables for importance to
perform variable selection, it is known that variance is
generally more harmful then bias \citep{piironen2017comparison}.}

\fede{In general, there is not restriction on the type of model the reference models 
should be and a sensible reference model does not need to be Bayesian.
However, Bayesian methods can help in some of those situations
where MLE procedures struggle. 
It is known that as the number of parameters in the model increases, the MLE
estimator is dominated by shrunk estimators 
\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
The use of a prior in Bayesian inference automatically incorporates 
some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
For the sake of our study, we rely on simple data structure which can be well described 
by linear regression models. However, more complex data can arise from applications, for example including hierarchical structures. In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the posterior distribution.}

We argue that, regardless of how
the reference model is set up and used in the inference procedure, it
can be always seen as acting as a filter on the observed
data. Furthermore, regardless of what specific model selection method
is used, a reference model can be used instead of raw data during the
selection process to improve the stability and selection
performance. Our results indicate that the core reason why the
reference model based methods perform well is the reference model
itself, rather than the specific way of using it.  In general, the
less data we have and the more complex the estimated models are, the
higher is the benefit of using a reference models as the basis for
variable selection.

@@
